The Weakly Nonlinear Magnetorotational Instability in a local geometry

### 2017-03-14 paper/thingap_ref_response/thingap_mri_paper_ref_response_apj.tex
fixed edit1 latex problem, it was choking on edit1 in a section header
dedalus acknowledged with software directive

\section{\edit1{Shearing box and ambipolar diffusion}}\label{sec:SBAD}

@@

@@

\section{Acknowledgments}
S.E.C. was supported by a National Science Foundation Graduate Research Fellowship under grant No. DGE-16-44869. J.S.O. acknowledges support from NASA grant \edit1{NNX16AC92G}. The authors thank Mordecai Mac Low, Jeremy Goodman, John Krommes, Geoff Vasil, and Ellen Zweibel for useful discussion.

>>>>

\section{Shearing box and ambipolar diffusion}\label{sec:SBAD}

@@

\section{Simulations}\label{sec:simulations}

\edit1{We perform nonlinear, axisymmetric simulations of our fiducial setup using Dedalus.}

@@

\section{Acknowledgments}
S.E.C. was supported by a National Science Foundation Graduate Research Fellowship under grant No. DGE-16-44869. J.S.O. acknowledges support from NASA grant \edit1{NNX16AC92G}. \edit1{We thank the anonymous referee for thoughtful comments that greatly improved the manuscript.} The authors thank Mordecai Mac Low, Jeremy Goodman, John Krommes, Geoff Vasil, and Ellen Zweibel for useful discussion. \software{Dedalus: http://dedalus-project.org/}
